% !TEX root = ..\..\..\..\main.tex
\subsubsection{Classifier learning method}
\label{sec:method:eval:param:learning}
Since the proposed model is designed to acquire deeper understanding for\todo{of} a concept for \todo{for each => for every passing}each iteration, it is important that \todo{that what the model}the model learns from is chosen in an appropriate manner. 25 images are presented each iteration and this evaluation is designed to decide \todo{how these 25 images should be selected}which setting that is the optimal one. The best setting in this benchmark is used in the evaluations that are performed later. 
The goal of the evaluation is to find a method that ensures that the model learns the concept as fast as possible but still perform well enough in order to reduce work for the user. 

Four distinct settings were chosen that are representative of how the data can be selected and still \todo{processes the dataset in an...}work through the data in an efficient manner. The different settings \todo{of the evaluation are}that were used are
\begin{enumerate}
	\item \textbf{Top20+Bottom5}: To present the 20 images that the classifier finds the most relevant and the 5 images that the classifier finds the \todo{least relevant}most irrelevant. As mentioned in Section \ref{sec:method:proposed:rf}, this is the how the model is designed to be present\todo{presented?} material.  
	\item \textbf{Top25}: To present the 25 images that the classifier finds the most relevant. 
	\item \textbf{Top20+Middle5}: To present the 20 images that the classifier finds the most relevant and the 5 images that are the closest to the decision boundary of the classifier. 
	\item \textbf{Top5+Bottom20}: To present the 5 images that the classifier finds the most relevant and the 20 images that the classifier finds the \todo{least relevant}most irrelevant. 
\end{enumerate}
In order to make the different settings deviate as much as possible, the model \todo{processed}classified the entire search space every iteration. Thus making the selection of images each iteration more predictable and the measurements\todo{add: of each setting} are less diverged in between the five different runs.

