% !TEX root = ..\main.tex
\chapter{Machine learning theory}
\label{chapter:mltheory}

This chapter introduces key concepts of the computer schience subfield machine learning. The chapter \todo{vill vi formulera det så här?}start \todokahl{Menar ni ``Starts off''?}of with a brief introduction\todokahl{Ofullständing mening} to machine learning, learning of the system\todo{learning of the system?} and classfication method used\todo{method used?}. Continues \todo{partial sentence}to present the idea of Support Vector Machine and its mechanics to end\todo{strange. The chapter ends the chapter.} the chapter with the focus on the SVM ensemble which is for getting a better performance\todo{not really why it is used.}. \\

% \section{Machine Learning}
% \label{sec:machine_learning}

Machine Learning is a field in computer science focused on methods where the computers learn without being explicitly programmed. Thus can be said to be the study and construction of algorithms that can learn from data and make predictions based upon it. In order for a person to learn about something new, the person looks back on previously learned knowledge and machine learning algorithms do not differ from this pattern. A famous quote that describes machine learning by Tom M. Mitchell is \textit{``A computer program is said to learn from experience E with respect to some class of tasks T and performance measure P, if its performance at tasks in T, as measured by P, improves with experience E''} \cite{Mitchell:1997:ML:541177}. 
Machine learning is applied to several different subjects in a number of different fields. Even though there are several learning methods and utilities of machine learning this thesis will only handle the concepts of supervised learning and in extension classification\todo{extension classification? What?}. Supervised learning will be used as it is most applicable \todo{Supervised learning will be used as it is most applicable? Necessary?} to the problem at hand as well as it is the learning method currently showing best results while one have ``labeled data''.\todo{and labeled data is often used to reward semi-supervised learning.}

%In machine learning the algorithms for deciding which data point that has which label behave very differently to achieve the goal but in the below sections the ba{}sics of the different paradigms, necessary for our method, are described. 

\input{include/machinelearningtheory/supervisedlearning}

\input{include/machinelearningtheory/classification}

\input{include/machinelearningtheory/svm}

\input{include/machinelearningtheory/ensemble}







